---
title: "BA_Assignment_3"
author: "Tejaswini Yeruva"
date: "2022-11-13"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1. Running the code that is provided.

```{r}
set.seed(2017) 
X=runif(100)*10 
Y=X*4+3.45 
Y=rnorm(100)*0.29*Y+Y
```

## a) Using plot function Y against X using the below command.

```{r}
cor(X,Y)
plot(X,Y)
```

## Since the Plot shows the positive correlation, Linear model can fit Y based on X.

## b) Simple linear model Y based on X.

```{r}
model<-lm(Y~X)
summary(model)
```
## The equation model is Y=3.6108*X+4.4655.

## Accuracy of the above linear model is 65.17%, above equation explains Y based on x.

## c) Coefficient of Determination
```{r}
(cor(Y,X))^2

## Coefficient of Determination= (Correlation Coefficient)^2
## Multiple R-square can be determined by squaring of correlation.

hist(model$residuals,freq = FALSE,ylim = c(0,0.05))
qqnorm(model$residuals,col="red")

## The above graph illustrates that the residuals are normally distrubuted, So the linear model is appropriate.

```

## 2) Using 'mtcars' dataset:
## a)
```{r}
head(mtcars)
summary(lm(hp~wt,data=mtcars))
summary(lm(hp~mpg,data=mtcars))
## By using the above linear model we see that the Multiple R-squared, mpg has high r square value 60% compared to wt of car i.e 43.95%

## Opinion made by Chris is right.
```

## b) 
```{r}
summary(model2<-lm(hp~cyl+mpg,data = mtcars))
((model2$coefficients[2]*4)+model2$coefficients[1])+(model2$coefficients[3]*22)
predict(model2,data.frame(cyl=4,mpg=22),interval = "prediction",level=0.85)
```

## 3) Installing the required package:
```{r}
library(mlbench)
data(BostonHousing)
```

## a) 
```{r}
hos<-lm(medv~crim+zn+ptratio+chas,data=BostonHousing)
summary(hos)
## R-Square value is very low i.e 36% by this we can tell that it is not an accurate model.
```

## b1)
```{r}
summary(hos1<-lm(medv~chas,data = BostonHousing))
hos1$coefficients
(hos1$coefficients[2]*0)+hos1$coefficients[1]
(hos1$coefficients[2]*1)+hos1$coefficients[1]
 ## From the above correlation coefficient, the house bound with Chas river is more expensive than the one not bound of 0 with value 4.3
```

## b2)
```{r}
summary(hos2<-lm(medv~ptratio,data = BostonHousing))
(hos2$coefficients[2]*15)+hos2$coefficients[1]
(hos2$coefficients[2]*18)+hos2$coefficients[1]

## From the above correlation coefficients, the coefficients are negative hence we can say that if the ptratio increases the housing price decreases.

## The price of house which has ptratio of 15 is more expensive compared to price of house which has a ptratio of 18 by 6.471

```

## c)
```{r}
summary(hos)
## A low p-value i.e < 0.05 tells that we can reject the null hypothesis.
## Hence from the model summary none of the independent variables are considerable.
```

## d)
```{r}
anova(hos)

## Order of importance of the values by comparing p values:
## 1) crim - Accounts for 15.08% 
## 2) ptratio - accounts for 11.02%
## 3) zn - accounts for 8.32%
## 4)chas - accounts for 1.56%

## In total the model accounts for 64.01 and it can be improved.

```

